---
title: "Consolidating Morphology Data"
author: "Elizabeth Byers"
date: "2025-03-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Load Data

```{r}
# Find nuclei files
nuclei <- list.files(path = "C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Nuclei", pattern = "[0-9]{2}_[0-9]{2}[a-z]{1}_Nuc_40x_[0-9]{1}_EditedNuclei.csv")
lamin <- list.files(path = "C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Nuclei", pattern = "[0-9]{2}_[0-9]{2}[a-z]{1}_NucLam_40x_[0-9]{1}_EditedNuclei.csv")
```

### Consolidate Nuclei Data ------------------------------

```{r}
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Nuclei")
# Load all NUCLEI csv's and combine into one dataframe
b <- data.frame()
for (h in 1:length(nuclei)) {
  a <- read.csv(nuclei[[h]])
  b <- rbind(a, b)
}
```

```{r}
# Export master NUCLEI dataframe
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Analysis")
write.csv(b, file = "All Nuclei Data.csv")
```

### Consolidate Nuclei with Lamin Data ------------------------------

```{r}
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Nuclei")
# Add surface and time point to individual csv's and save them.  This must be done before combining all csv's into one large dataframe.
for (i in 1:length(lamin)) {
 csv <- read.csv(lamin[[i]])
 csv$Surface <- rep(substring(lamin[[i]], first = 1, last = 2), nrow(csv))
 csv$Time.Point <- rep(substring(lamin[[i]], first = 4, last = 6), nrow(csv))
 write.csv(csv, file = lamin[[i]])
}
```

```{r}
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Nuclei")
# Load all NUCLAM csv's and combine into one dataframe
d <- data.frame()
for (j in 1:length(lamin)) {
  c <- read.csv(lamin[[j]])
  d <- rbind(c, d)
}
```

```{r}
# Export master NUCLEI and LAMIN dataframe
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Analysis")
write.csv(d, file = "All Nuclei and Lamin Data.csv")
```



### Consolidate Cell Body Data ----------------------------

```{r}
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Cell Body 2026")
# Add surface and time point to individual CELL BODY information csv's and save them.  This must be done before combining all csv's into one large dataframe.
body <- list.files(path = "C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Cell Body 2026", pattern = "[0-9]{2}_[0-9]{2}[a-z]{1}_[0-9]{1}_Cells.csv")
for (i in 1:length(body)) {
 csv.b <- read.csv(body[[i]])
 csv.b$Surface <- rep(substring(body[[i]], first = 1, last = 2), nrow(csv.b))
 csv.b$Time.Point <- rep(substring(body[[i]], first = 4, last = 6), nrow(csv.b))
 write.csv(csv.b, file = body[[i]])
}
```

```{r}
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Cell Body 2026")
# Load all CELL BODY csv's and combine into one dataframe
e <- data.frame()
for (k in 1:length(body)) {
  f <- read.csv(body[[k]])
  e <- rbind(e, f)
}
```

```{r}
e$Time.Point <- gsub("24h", "24 Hours", e$Time.Point)
e$Time.Point <- gsub("07d", "7 Days", e$Time.Point)
e$Time.Point <- gsub("14d", "14 Days", e$Time.Point)
e$Time.Point <- factor(e$Time.Point, levels = c("24 Hours", "7 Days", "14 Days"))
e$Surface <- gsub(3, "3%", e$Surface)
e$Surface <- gsub(4, "4%", e$Surface)
e$Surface <- gsub(6, "6%", e$Surface)
e$Surface <- gsub(7, "7%", e$Surface)
e$Surface <- gsub(8, "8%", e$Surface)
e$Surface <- gsub(10, "10%", e$Surface)
e$Surface <- gsub(0, "Control", e$Surface)
e$Surface <- gsub("1Control%", "10%", e$Surface)
e$Surface <- factor(e$Surface, levels = c("Control", "3%", "4%", "6%", "7%", "8%", "10%"))
```

```{r}
# Export master CELL BODY dataframe
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/R Files")
write.csv(e, "Completed Cell Body Dataset.csv")
```


### Reload and Clean Master Dataframes ----------------------
Nuclei only data

```{r}
nuc <- read.csv("All Nuclei Data.csv")
```

```{r}
library(dplyr)
library(tidyselect)
```

```{r}
# nuc <- nuc[, colSums(is.na(nuc)) != 0]
not_all_na <- function(x) any(!is.na(x))
nuc <- select(nuc, where(not_all_na))
```

```{r}
nuc$Time.Point <- gsub("24h", "24 Hours", nuc$Time.Point)
nuc$Time.Point <- gsub("07d", "7 Days", nuc$Time.Point)
nuc$Time.Point <- gsub("14d", "14 Days", nuc$Time.Point)
nuc$Time.Point <- factor(nuc$Time.Point, levels = c("24 Hours", "7 Days", "14 Days"))
nuc$Surface <- gsub(0, "Control", nuc$Surface)
nuc$Surface <- gsub(6, "6%", nuc$Surface)
nuc$Surface <- gsub(7, "7%", nuc$Surface)
nuc$Surface <- gsub(8, "8%", nuc$Surface)
nuc$Surface <- gsub("1Control", "10%", nuc$Surface)
nuc$Surface <- factor(nuc$Surface, levels = c("Control", "6%", "7%", "8%", "10%"))
```

```{r}
# Ensure there are no NAs left that may have been introduced during binding rows or substitutions
nuc <- nuc[!is.na(nuc$Surface), ]
write.csv(nuc, file = "All Nuclei Data.csv")
```

Lamin only data

```{r}
lam <- read.csv("All Nuclei and Lamin Data.csv")
```

```{r}
lam <- lam[, 5:238]
```

```{r}
lam$Time.Point <- gsub("24h", "24 Hours", lam$Time.Point)
lam$Time.Point <- gsub("07d", "7 Days", lam$Time.Point)
lam$Time.Point <- gsub("14d", "14 Days", lam$Time.Point)
lam$Time.Point <- factor(lam$Time.Point, levels = c("24 Hours", "7 Days", "14 Days"))
lam$Surface <- gsub(0, "Control", lam$Surface)
lam$Surface <- gsub(6, "6%", lam$Surface)
lam$Surface <- gsub(7, "7%", lam$Surface)
lam$Surface <- gsub(8, "8%", lam$Surface)
lam$Surface <- gsub("1Control", "10%", lam$Surface)
lam$Surface <- factor(lam$Surface, levels = c("Control", "6%", "7%", "8%", "10%"))
```

```{r}
# Ensure there are no NAs left that may have been introduced during binding rows or substitutions
lam <- select(lam, where(not_all_na))
write.csv(lam, file = "All Nuclei and Lamin Data.csv")
```

Try to combine all nucleus data into one data frame

```{r}
nuc <- read.csv("All Nuclei Data.csv")
lam <- read.csv("All Nuclei and Lamin Data.csv")
```

```{r}
combined <- full_join(nuc, lam)
write.csv(combined, "Combined Nuclei Data as of 3-31-25.csv")
```


```{r}
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Nuclei")
files <- list.files(path = wd, pattern = "[0]{1}[3-4]{1}_[0-9]{2}[a-z]{1}_Nuc_40x_[0-9]{1}_EditedNuclei.csv")
```

```{r}
# Add surface and time point to individual csv's and save them.  This must be done before combining all csv's into one large dataframe.
for (i in 1:length(files)) {
 csv <- read.csv(files[[i]])
 csv$Surface <- rep(substring(files[[i]], first = 1, last = 2), nrow(csv))
 csv$Time.Point <- rep(substring(files[[i]], first = 4, last = 6), nrow(csv))
 write.csv(csv, file = files[[i]])
}
```

```{r}
# Load all csv's and combine into one dataframe
b <- data.frame()
for (j in 1:length(files)) {
  a <- read.csv(files[[j]])
  b <- rbind(a, b)
}
```

```{r}
b$Time.Point <- gsub("24h", "24 Hours", b$Time.Point)
b$Time.Point <- gsub("07d", "7 Days", b$Time.Point)
b$Time.Point <- gsub("14d", "14 Days", b$Time.Point)
b$Time.Point <- factor(b$Time.Point, levels = c("24 Hours", "7 Days", "14 Days"))
b$Surface <- gsub(3, "3%", b$Surface)
b$Surface <- gsub(4, "4%", b$Surface)
b$Surface <- factor(b$Surface, levels = c("3%", "4%"))
```

```{r}
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cell Profiler Results/Nuclei")
files <- list.files(path = wd, pattern = "[0]{1}[3-4]{1}_[0-9]{2}[a-z]{1}_NucLam_40x_[0-9]{1}_EditedNuclei.csv")
```

```{r}
# Add surface and time point to individual csv's and save them.  This must be done before combining all csv's into one large dataframe.
for (i in 1:length(files)) {
 csv <- read.csv(files[[i]])
 csv$Surface <- rep(substring(files[[i]], first = 1, last = 2), nrow(csv))
 csv$Time.Point <- rep(substring(files[[i]], first = 4, last = 6), nrow(csv))
 write.csv(csv, file = files[[i]])
}
```

```{r}
# Load all csv's and combine into one dataframe
b <- data.frame()
for (j in 1:3) {
  a <- read.csv(files[[j]])
  b <- rbind(a, b)
}
c <- data.frame()
for (k in 4:6) {
  d <- read.csv(files[[k]])
  c <- rbind(d, c)
}
```

```{r}
b$Time.Point <- gsub("24h", "24 Hours", b$Time.Point)
b$Time.Point <- gsub("07d", "7 Days", b$Time.Point)
b$Time.Point <- gsub("14d", "14 Days", b$Time.Point)
b$Time.Point <- factor(b$Time.Point, levels = c("24 Hours", "7 Days", "14 Days"))
b$Surface <- gsub(3, "3%", b$Surface)
b$Surface <- gsub(4, "4%", b$Surface)
b$Surface <- factor(b$Surface, levels = c("3%", "4%"))

c$Time.Point <- gsub("24h", "24 Hours", c$Time.Point)
c$Time.Point <- gsub("07d", "7 Days", c$Time.Point)
c$Time.Point <- gsub("14d", "14 Days", c$Time.Point)
c$Time.Point <- factor(c$Time.Point, levels = c("24 Hours", "7 Days", "14 Days"))
c$Surface <- gsub(3, "3%", c$Surface)
c$Surface <- gsub(4, "4%", c$Surface)
c$Surface <- factor(c$Surface, levels = c("3%", "4%"))
```

```{r}
# Ensure there are no NAs left that may have been introduced during binding rows or substitutions
total2 <- b[!is.na(b$Surface), ]
total3 <- c[!is.na(c$Surface), ]
```

```{r}
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/R Files")
previous.data <- read.csv("Combined Nuclei Data as of 3-31-25.csv")
```


```{r}
# combined1 <- full_join(total, total2)
# combined2 <- full_join(combined1, total3)
# combined3 <- full_join(combined2, previous.data)
write.csv(combined3, "Completed Nuclei and Lamin Dataset.csv")
```

### Consolidate Cadherin Data ----------------------------

#### Control Surfaces

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/Control/24 Hours")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df <- bind_rows(myfiles)
df <- bind_cols(df, rep.int("Control", length(df$X)), rep.int("24 Hours", length(df$X)))
names(df)[18] <- "Surface"
names(df)[19] <- "TimePoint"
df <- df[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/Control/7 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df2 <- bind_rows(myfiles)
df2 <- bind_cols(df2, rep.int("Control", length(df2$X)), rep.int("7 Days", length(df2$X)))
names(df2)[18] <- "Surface"
names(df2)[19] <- "TimePoint"
df2 <- df2[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/Control/14 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df3 <- bind_rows(myfiles)
df3 <- bind_cols(df3, rep.int("Control", length(df3$X)), rep.int("14 Days", length(df3$X)))
names(df3)[18] <- "Surface"
names(df3)[19] <- "TimePoint"
df3 <- df3[, 2:19]
```

#### 6% Surfaces

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/6%/24 Hours")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df4 <- bind_rows(myfiles)
df4 <- bind_cols(df4, rep.int("6%", length(df4$X)), rep.int("24 Hours", length(df4$X)))
names(df4)[18] <- "Surface"
names(df4)[19] <- "TimePoint"
df4 <- df4[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/6%/7 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df5 <- bind_rows(myfiles)
df5 <- bind_cols(df5, rep.int("6%", length(df5$X)), rep.int("7 Days", length(df5$X)))
df5 <- df5[, -c(18:19)]
names(df5)[18] <- "Surface"
names(df5)[19] <- "TimePoint"
df5 <- df5[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/6%/14 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df6 <- bind_rows(myfiles)
df6 <- bind_cols(df6, rep.int("6%", length(df6$X)), rep.int("14 Days", length(df6$X)))
names(df6)[16] <- "Surface"
names(df6)[17] <- "TimePoint"
df6 <- df6[, 2:17]
```

#### 7% Surfaces

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/7%/24 Hours")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df7 <- bind_rows(myfiles)
df7 <- bind_cols(df7, rep.int("7%", length(df7$X)), rep.int("24 Hours", length(df7$X)))
names(df7)[18] <- "Surface"
names(df7)[19] <- "TimePoint"
df7 <- df7[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/7%/7 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df8 <- bind_rows(myfiles)
df8 <- bind_cols(df8, rep.int("7%", length(df8$X)), rep.int("7 Days", length(df8$X)))
names(df8)[18] <- "Surface"
names(df8)[19] <- "TimePoint"
df8 <- df8[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/7%/14 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df9 <- bind_rows(myfiles)
df9 <- bind_cols(df9, rep.int("7%", length(df9$X)), rep.int("14 Days", length(df9$X)))
names(df9)[18] <- "Surface"
names(df9)[19] <- "TimePoint"
df9 <- df9[, 2:19]
```

#### 8% Surfaces

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/8%/24 Hours")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df10 <- bind_rows(myfiles)
df10 <- bind_cols(df10, rep.int("8%", length(df10$X)), rep.int("24 Hours", length(df10$X)))
names(df10)[18] <- "Surface"
names(df10)[19] <- "TimePoint"
df10 <- df10[, 2:19]
```

```{r}
# Set working directory - NO CADHERIN 8% 7 DAYS 
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/8%/7 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df11 <- bind_rows(myfiles)
df11 <- bind_cols(df11, rep.int("8%", length(df11$X)), rep.int("7 Days", length(df11$X)))
names(df11)[18] <- "Surface"
names(df11)[19] <- "TimePoint"
df11 <- df11[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/8%/14 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df12 <- bind_rows(myfiles)
df12 <- bind_cols(df12, rep.int("8%", length(df12$X)), rep.int("14 Days", length(df12$X)))
names(df12)[18] <- "Surface"
names(df12)[19] <- "TimePoint"
df12 <- df12[, 2:19]
```

#### 10% Surfaces

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/10%/24 Hours")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df13 <- bind_rows(myfiles)
df13 <- bind_cols(df13, rep.int("10%", length(df13$X)), rep.int("24 Hours", length(df13$X)))
names(df13)[18] <- "Surface"
names(df13)[19] <- "TimePoint"
df13 <- df13[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/10%/7 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df14 <- bind_rows(myfiles)
df14 <- bind_cols(df14, rep.int("10%", length(df14$X)), rep.int("7 Days", length(df14$X)))
names(df14)[16] <- "Surface"
names(df14)[17] <- "TimePoint"
df14 <- df14[, 2:17]
```

```{r}
# Set working directory - NO CADHERIN 10% 7 DAYS 
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/10%/14 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df15 <- bind_rows(myfiles)
df15 <- bind_cols(df15, rep.int("10%", length(df15$X)), rep.int("14 Days", length(df15$X)))
names(df15)[18] <- "Surface"
names(df15)[19] <- "TimePoint"
df15 <- df15[, 2:19]
```

#### 3% Surfaces

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/3%/24 Hours")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df16 <- bind_rows(myfiles)
df16 <- bind_cols(df16, rep.int("3%", length(df16$X)), rep.int("24 Hours", length(df16$X)))
names(df16)[18] <- "Surface"
names(df16)[19] <- "TimePoint"
df16 <- df16[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/3%/7 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df17 <- bind_rows(myfiles)
df17 <- bind_cols(df17, rep.int("3%", length(df17$X)), rep.int("7 Days", length(df17$X)))
names(df17)[18] <- "Surface"
names(df17)[19] <- "TimePoint"
df17 <- df17[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/3%/14 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df18 <- bind_rows(myfiles)
df18 <- bind_cols(df18, rep.int("3%", length(df18$X)), rep.int("14 Days", length(df18$X)))
names(df18)[18] <- "Surface"
names(df18)[19] <- "TimePoint"
df18 <- df18[, 2:19]
```

#### 4% Surfaces

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/4%/24 Hours")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df19 <- bind_rows(myfiles)
df19 <- bind_cols(df19, rep.int("4%", length(df19$X)), rep.int("24 Hours", length(df19$X)))
names(df19)[18] <- "Surface"
names(df19)[19] <- "TimePoint"
df19 <- df19[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/4%/7 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df20 <- bind_rows(myfiles)
df20 <- bind_cols(df20, rep.int("4%", length(df20$X)), rep.int("7 Days", length(df20$X)))
names(df20)[18] <- "Surface"
names(df20)[19] <- "TimePoint"
df20 <- df20[, 2:19]
```

```{r}
# Set working directory
wd <- setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/Thesis Studies/Cadherin ImageJ Analysis/4%/14 Days")
# Load all csv's
temp <- list.files(pattern="\\.csv$")
myfiles <- lapply(temp, read.csv)
# Combine all tables together
df21 <- bind_rows(myfiles)
df21 <- bind_cols(df21, rep.int("4%", length(df21$X)), rep.int("14 Days", length(df21$X)))
names(df21)[18] <- "Surface"
names(df21)[19] <- "TimePoint"
df21 <- df21[, 2:19]
```

### Combine individual dataframes from each surface and time point into one master dataframe

```{r}
combined16 <- bind_rows(df6, df14)
combined18 <- bind_rows(df, df2, df3, df4, df5, df7, df8, df9, df10, df12, df13, df16, df17, df18, df19, df20, df21)
```

```{r}
combined.and.reduced16 <- combined16[, c(1:4, 6, 12:16)]
combined.and.reduced18 <- combined18[, c(1:4, 6, 14:18)]
combined.all <- bind_rows(combined.and.reduced16, combined.and.reduced18)
```

```{r}
# Fix factor level issues
combined.all$Surface <- factor(combined.all$Surface, levels = c("Control", "3%", "4%", "6%", "7%", "8%", "10%"))
combined.all$TimePoint <- factor(combined.all$TimePoint, levels = c("24 Hours", "7 Days", "14 Days"))
```

```{r}
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/R Files")
write.csv(combined.all, file = "Completed Cadherin Dataset.csv", col.names = T)
```

```{r}
setwd("C:/Users/erbye/OneDrive - The Pennsylvania State University/Data/R Files")
vin.data <- read.csv("Completed Vinculin Dataset.csv", header = T)
cad.data <- read.csv("Completed Cadherin Dataset.csv", header = T)
```


